Approximation as Differentiation: Notes

### 2025-05-19 notes/cmon-enriched.tex
WIP.

The $\CMon$-enriched Yoneda embedding preserves biproducts, where (as in any functor category) biproducts in
$\PSh_{\CMon}(\cat{C})$ are computed pointwise.

>>>>

The $\CMon$-enriched Yoneda embedding \todo{think this works for any monoidal closed $\mathscr{V} with
biproducts?$} preserves biproducts, where (as in any functor category) biproducts in $\PSh_{\CMon}(\cat{C})$
are computed pointwise, and noting that $\CMon$ itself has biproducts.
